The Hydrogen Epoch of Reionization Array Dish I: Beam Pattern Measurements and Science Implications

### 2015-11-07 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex

design principles
tradeoffs
description of the final design

We compare measured beam patterns with a simplistic analytic model and two numerical electromagnetic models. Briefly, the dish is constructed of overlapping mesh rectangles secured to hanging PVC pipes to form an approximately parabolic surface with diameter 14\,m. The feed consists of a dual-polarization dipole antenna with a circular mesh backplane and a cylindrical mesh ``skirt'' hanging down. The feed is suspended over the dish surface by three ropes attached to poles equally spaced around the dish.

\begin{enumerate}
	\item Airy pattern for a 14\,m aperture
	\item CST simulation (hera-cst/HERA\_DISH\_paper \_feed\_cyl36\_140mhz\_Y\_healpix.fits)
	\item A separate simulation run by Dave with 68'' diameter feed backplane and 26'' skirt.
\end{enumerate}

\section{Error Analysis}

@@

@@

\section{Dish Characterization}

>>>>

\subsection{Assessing Experimental Systematics}

@@

ASK DAVE DEBOER TO WRITE A TWO PARAGRAPH SUMMARY OF THE HERA ELEMENT AND HOW IT WAS DESIGNED

ASK DAVE OR RICH TO WRITE A ONE OR TWO PARAGRAPH SUMMARY OF THE ELECTROMAGNETIC DISH SIMULATIONS

@@

\section{Dish Measurements}
